\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{parskip} % To handle paragraph spacing more easily

\title{An Open Letter to the Republican Party}
\author{by Pedro Dominguez}
\date{May 31, 2023} % Setting the date as requested

\begin{document}

\maketitle % This command prints the title, author, and date

Dear Members of the Republican Party,

\vspace{1em} % Adds a bit of vertical space

I am Pedro Dominguez, a proud 27-year-old supporter of the GOP, and I wish to extend my technical expertise to the Republican Party and its members, whether as a pro bono contributor or in a compensated capacity. My proficiency encompasses programming languages, ChatGPT Plus, large language models, GPT-4 API, website deployment, and domain management.

Originally from Ciudad Juarez, Mexico, I relocated to Oklahoma City at the age of five, which has been my home ever since. I graduated high school in this vibrant city and am eager to pursue a degree in computer science, driven by my passion for the field. Ultimately, I aspire to harness my skills to shape a brighter future for all Americans, irrespective of their political leanings.

As the 2024 Election draws near, capturing the Gen Z vote is paramount for the Republican Party. As a Gen Z member, I am convinced that my expertise will facilitate the GOP’s outreach to younger voters and foster enduring connections. My unique perspective as a young, technologically adept immigrant holds the potential to substantially impact the party’s success in the forthcoming election.

Nonetheless, I must acknowledge that I am currently grappling with some challenges. As a beneficiary of the Deferred Action for Childhood Arrivals (DACA) program, I require assistance in renewing my work permit. Moreover, I am striving to settle outstanding rent and bills. While I recognize the personal nature of these concerns, I hope you can discern the potential value of my contributions to the party and aid me in surmounting these hurdles. Once I regain stability, I am committed to generating income through various avenues.

Additionally, I would like to mention that I have been dedicatedly caring for my 65-year-old mother, who is a resilient breast cancer survivor. She has successfully completed chemotherapy, radiation, and physical therapy, and I have been by her side throughout this challenging journey. My experience in supporting my mother’s recovery further demonstrates my commitment to family values and compassion for others, qualities that I believe align with the core principles of the Republican Party.

In conclusion, I am offering my skills and expertise as a young, ambitious immigrant with a robust technical background to the Republican Party. With your support, I am confident that I can help the GOP secure the Gen Z vote in the 2024 Election and contribute to the party’s overall success. I kindly request your help in addressing my present challenges and, in return, pledge to work diligently to advance the Republican Party’s objectives.

Thank you for considering my offer. I eagerly anticipate your response and the prospect of collaborating to forge a brighter future for our great nation.

Sincerely,

Pedro Dominguez

\end{document}
