\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{mathpazo} % Adds the palatino font with some nice cursive fonts
\geometry{a4paper, margin=1in}
\usepackage{parskip}

\begin{document}

\hfill December 6, 2023

\vspace{2em}

\begin{center}
\textbf{Open Letter to the Republican Party}
\end{center}

\vspace{1em}

Dear Members of the Republican Party,

\vspace{1em}

My name is Pedro Dominguez, a young dreamer who has embraced the ethos of the American Dream. Born on September 26, 1995, in Ciudad Juárez, Mexico, I was brought to the United States in December 1999, at the age of five. As a 28-year-old currently studying at Oklahoma City Community College, my goal is to obtain a bachelor's degree in Computer Science. This aspiration is deeply intertwined with the values that epitomize the spirit of conservative America.

Throughout my life in the U.S., I have adhered to the principles of hard work, integrity, and a dedication to excellence, values that resonate with the core ideals of the Republican Party. Despite facing numerous challenges, my commitment to contributing positively to American society has only been reinforced.

My ambition to delve into the world of Artificial Intelligence and contribute to technological advancements in our nation is, however, hindered by the uncertainties surrounding my DACA status. The renewal of my DACA application is not just a legal formality; it is a crucial step that enables me to afford my tuition and continue my education. Without this renewal, my academic and professional aspirations could be irreparably halted.

Thus, I humbly request your support in renewing my DACA status. This support is more than just an aid for an individual; it is an investment in a future that holds the promise of American innovation, technological leadership, and the embodiment of the conservative values of individual initiative and societal progress.

I understand the complexities of immigration policy and the diverse opinions within our party. Yet, I believe that my story underscores the potential of bipartisan collaboration in creating opportunities for young people like me, who are eager to contribute to our society and uphold the values we all cherish.

In closing, I appeal to your sense of community and practicality. Assisting individuals like myself is a testament to the American spirit of opportunity, transcending political divisions and uniting us in our shared goal of a prosperous, forward-thinking nation.

Thank you for considering my appeal. I remain hopeful and committed to playing an integral role in building a brighter future for all Americans.

\vspace{2em}

Sincerely,

\vspace{2em}

\hfill \textit{\large Pedro Dominguez} % Cursive-like font for the name

\hfill December 6, 2023

\end{document}
